---
name: Midori
surname: Yajima
position: "Visiting Researcher"
address: "Trinity College Dublin"
phone: +39 338 122 3976
email: "yajimamidorimichela@gmail.com"
twitter: yajimamidori
github: midoriyajima
linkedin: midori-yajima
date: "`r format(Sys.time(), '%B %Y')`"
output: 
  vitae::moderncv:
    theme: classic
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(tidyverse)
library(glue)
library(kableExtra)
library(tibble)
library(knitr)
```

I am an MSc graduate in ecology - ecosystem and conservation biology with a BSc in biological sciences and a keen interest in exploring how human and environmental systems intersect

# Education

```{r}
edu <- read.csv("~/CV/CV/Data/Education.csv")

edu %>% 
  detailed_entries(
    what = degree,
    when = glue("{start_date} - {end_date}"),
    with = glue("{university}, {location}"),
    why = glue("Dissertation: {dissertation},
               Grade: {grade}")
  )
                 
```
# Research experience

```{r}
exp <- read.csv("~/CV/CV/Data/Research-experience.csv")

exp %>% 
  detailed_entries(
    what = role,
    when = glue("{start_date} - {end_date}"),
    with = glue("{institution}, {location}"),
    why = description
  )

```

# Courses and workshops

```{r}
courses <- read.csv("~/CV/CV/Data/Courses and workshops.csv")

courses %>% 
  detailed_entries(
    what = name,
    when = date,
    with = who
    )

```

# Awards and scholarships

```{r}
aws <- read.csv("~/CV/CV/Data/Awards and Scholarships.csv")

aws %>% 
  detailed_entries(
    what = name,
    when = when,
    why = description,
    with = who,
  )

```

# Talks and presentations
## Academic

```{r}
talks <- read.csv("~/CV/CV/Data/Talks and Presentations.csv")

talks %>% 
  filter(what == "Academic Presentation") %>% 
  brief_entries(name, date)

```
## Non academic

```{r}
talks <- read.csv("~/CV/CV/Data/Talks and Presentations.csv")

talks %>% 
  filter(what == "Non academic") %>% 
  brief_entries(name, date)

```

# Outreach
## Written contents

```{r}
out <- read.csv("~/CV/CV/Data/Outreach.csv")

out %>% 
  filter(what == "Written contents") %>% 
  brief_entries(name)

```

## Visual contents

```{r}
out <- read.csv("~/CV/CV/Data/Outreach.csv")

out %>% 
  filter(what == "Visual contents") %>% 
  brief_entries(name)

```

## Activities and events

```{r}
out <- read.csv("~/CV/CV/Data/Outreach.csv")

out %>% 
  filter(what == "Events") %>% 
   brief_entries(glue("{description} - {name}")
   )

```

# Mentoring

```{r}
ment <- read.csv("~/CV/CV/Data/Mentoring.csv")

ment %>% 
   brief_entries(description, ifelse(end_date == "",
                  start_date,
                  glue("{start_date} - {end_date}")
    )
  )

```
# Other experiences
```{r}
other <- read.csv("~/CV/CV/Data/Other experience.csv")

other %>% 
  detailed_entries(
    what = role, 
    when = glue("{start_date} - {end_date}"),
    with = where,
    why = details
  )

```
# Media coverage
```{r}
media <- read.csv("~/CV/CV/Data/Media coverage.csv")

media %>% 
 brief_entries(name)

```

\newpage

# Skills
## Technical
|                     **Programming** (R, RStudio, Rmarkdown, Shiny apps) 
|                     **Geographic Information Systems** (QGIS)
|                     **Graphic design** (Adobe Photoshop, Adobe Illustrator)
|                     **Reference management** (Mendeley, Colandr)
|                     **Collaboration skills** (Miro, GitHub)

## Professional
|                     Energy Dispersive and Backscattered **Electron Scanning Microscopy**  
|                     Production of **archival quality plant specimens**
|                     Use of **field equipment** (thermohygrometer, porometer, fluorometer,
|                     ceptometer)
|                     Exploratory **data analysis**, data **visualisation**, data
|                     **management**

## Language
|                     Italian (Mother tongue), English (Advanced), Portuguese (Intermediate), 
|                     Spanish (Base), French (Base)

# References
|                    Professor **Jennifer McElwain**, Chair of Botany
|                      at Trinity College Dublin's School of Natural
|                      Sciences and director of Trinity College Botanic
|                      Garden 
|                      jmcelwai@tcd.ie
|                      https://www.tcd.ie/Botany/people/JMCELWAI/
|                      https://plantclimatelab.ie/

&nbsp;

|                    Doctor **Suzette Flantua** research fellow at
|                      University of Bergen and Project leader of
|                      PPF-Alpine 
|                      suzette.flantua@uib.no
|                      https://www.uib.no/en/persons/Suzette.Geertruida.Anna.Flantua  
|                      https://mountainsinmotion.w.uib.no/  